Wykorzystanie Ethereum do Budowy Zdecentralizowanej Aplikacji

### 2018-04-06 article.tex
Better fix keywords translation + upercase title
It's time to create some content

\documentclass[runningheads]{llncs}

@@

\renewcommand{\keywords}[1]{
    \def\and{* }
    \begingroup
    \par
    \bigskip
    \noindent\textbf{Słowa Kluczowe: } #1\par
    \endgroup
}

@@

\title{Wykorzystanie Ethereum do budowy zdecentralizowanej aplikacji}
\author{Wojciech Korzeniowski}
\institute{
  Instytut Informatyki\\Wydział Elektroniki i Technik Informacyjnych\\Politechnika Warszawska\\
  \url{http://www.ii.pw.edu.pl/}
}

@@

\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

@@

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
  x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{theorem}
  This is a sample theorem. The run-in heading is set in bold, while
  the following text appears in italics. Definitions, lemmas,
  propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
  Proofs, examples, and remarks have the initial word in italics,
  while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
  \bibitem{ethereum} Ethereum Homepage, \url{https://www.ethereum.org/}
\end{thebibliography}
\end{document}

>>>>

\documentclass[]{llncs}

@@

% Translate some names to polish
\def\keywordname{{\bf Słowa Kluczowe:}}

@@

\title{Wykorzystanie Ethereum do Budowy Zdecentralizowanej Aplikacji}
\author{Wojciech Korzeniowski}
\institute{
  Instytut Informatyki\\Wydział Elektroniki i Technik Informacyjnych\\Politechnika Warszawska\\
  \url{http://www.ii.pw.edu.pl/}
}

@@

\section{First Section}
\subsection{Second Section}
\subsubsection{Third Section}
\paragraph{Fourth Level}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
  \bibitem{ethereum} Ethereum Homepage, \url{https://www.ethereum.org/}
\end{thebibliography}

% ########## START OF SAMPLES

\newpage
\newpage

\section{Takie tam przydatne przykłady}
\begin{definition} text \end{definition}
\begin{case} text \end{case}
\begin{proof} text \end{proof}

\noindent Widać na równaniu:
\begin{equation}
  x + y = z
\end{equation}

Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

Tabla~\ref{tab1} przedstawia że działa.

@@

% ########## END OF SAMPLES

\end{document}
